---
title: "workshop9-collab"
format: html
---

load libraries

```{r}
library(tidyverse) # for wrangling and plotting
library(lterdatasampler) # for data access
library(ggeffects) # for models
library(here) # for easy file pathing
```

reading in data:

```{r}
data(pie_crab) # reading in plum island ecosystem crab data set from lterdatasampler package
```

exploratory vis

```{r}
ggplot(aes(x= latitude, y = size), data= pie_crab) + # set up plot
  geom_point(color = "orange") + # scatterplot, and make it orange
  labs(x = "Latitude", y = "Size (mm)") + # update axes labels
  theme_minimal() # remove gridlines by updating theme
```

writing a model

```{r}
crab_model <- lm(size ~ latitude, # formula: response ~ predictor
                 data = pie_crab) # data from lter data sampler

# look at diagnostics here
par(mfrow = c(2, 2)) # plot the diagnostic plots in a 2x2 grid
plot(crab_model) # plotting the diagnostics
```

interpret model!

```{r}
summary(crab_model) #look at results
```

Slope: 0.49 +/- 0.034
Y intercept: -3.6 +/- 1.27

For every one unti increase in latitude, we expect to see an increase in crab size of 0.49 +/- 0.034 mm.

model statistics: F(1,390) = 208.5, p < 0.0001, alpha = 0.05, R^2^ = 0.35

General tips for collaboration:  
1. ALWAYS SAVE AND COMMIT AND PUSH!!!!!! do this often!!!!!!!!!!!!  
2. TALK TO YOUR COLLABORATORS  
3. PULL CHANGES!!!!!!!! otherwise you will get a "merge conflict"  

order of operations:
pull, work, save, stage, commit, push



